Projecting genetic associations through gene expression patterns highlights disease etiology and drug mechanisms

### 2023-06-28 output/latex/manuscript.tex
update data availability statement

>>>>

The data used from PhenomeXcan, LINCS L1000, and MultiPLIER are publicly available.
All significant results reported for the eMERGE and Penn Medicine BioBank (PMBB) phenome-wide TWAS are contained in\textsuperscript{\protect\hyperlink{ref-gZAOkumx}{27}}.
The individual-level PMBB raw datasets can not be made publicly available due to institutional privacy policy.
Please contact Penn Medicine Biobank (\url{https://pmbb.med.upenn.edu/pmbb/}) for requests of access to data.
eMERGE network phase III data is available on dbGAP (Accession: phs001584.v2.p2).
